\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-12-06 Final Paper/PaperJLin.tex
Expanded Literature Review

In general, the possibilities of social interactions between people in a specific vicinity  matters in how they will form their political attitudes. Early research in this field \citep{glenn_rural-urban_1967} shows that rural residents are less trusting of their neighbors than their urban counterparts.  In a more recent study using 2000 Census data in the United States, the research suggests that diversity is a great factor influencing liberal views, or lack thereof \citep{williamson_sprawl_2008}. When people are in places where diversity is vibrant, they are more likely to be open to newer experiences. Yet, this is most likely, in modern times, an occurrence of the urban centers and less so once one moves to the margins of geographic space in society. Therefore, space matters in the opportunities for attitude development because it facilitates one's exposure to diversity and opens the door to possibilities.

@@

>>>>

To begin, the link between place and political ideology varies with the qualities of the individual \citep{orbell_impact_1970}. Education, income and previous places of residence, among others, shape the individual's course of live and exposure to information and additional political ideologies and attitudes. This is seen in a case study of the people of Zimbabwe's Eastern Highlands \citep{moore_subaltern_1998}. Here, people developed attitudes towards their country and government based on the ways that they were raised and the varieties of environments that they had been exposed to as they grew up. Familial socioeconomic factors would proceed to influence the ways that these lessons and views would be passed down to their children, and shared with the village.

While personal factors matter to determine the development of one's morals and perceptions of political efficacy, comparative case studies on six European countries suggest that trends of globalization, along with its components of economic and social competition, can influence not only the development of a party system in a country, but also shape the viewpoints of the people in it \citep{kriesi_globalization_2006}. When party systems developed during Europian countries' transition to democracy, the people were lined on interests based on their stance on economic and social issues. As \cite{walsh_putting_2012} implies, place influences one's development of their stances on these issues, thereby leading place of residence to have the potential of influencing the survival of political parties.

In general, the possibilities of social interactions between people in a specific vicinity matters in how they will form their political attitudes. Early research in this field \citep{glenn_rural-urban_1967} shows that rural residents are less trusting of their neighbors than their urban counterparts.  In a more recent study using 2000 Census data in the United States, the research suggests that diversity is a great factor influencing liberal views, or lack thereof \citep{williamson_sprawl_2008}. When people are in places where diversity is vibrant, they are more likely to be open to newer experiences. Yet, this is most likely, in modern times, an occurrence of the urban centers and less so once one moves to the margins of geographic space in society. Therefore, space matters in the opportunities for attitude development because it facilitates one's exposure to diversity and opens the door to possibilities. Yet, at the same time, the state of development of the country on it's path to democracy, along with the political participation of the individual residents, also contribute to the connections between place of residence and political ideology.

@@

The coding of a place of residence largely lies in the hearts and minds of the individual respondent. While the CSES works to define the circumstances that will differenciate one region from another in order to standardize the results, there are, nonetheless, both individual and country differences in codifying the definitions of each place. For example, the definition of urban in Japan is any place with more than 200,000 people whereas in Israel, an urban place of residence means that the respondent lives in Tel-Aviv, Jerusalem, or Haifa. Rural areas are often more uniformly defined as any place, once translated from the language of the survey, to be an area sparsely populated.
